Unifying intraspecific and interspecific variation in tropical tree mortality

### 2016-06-10 ms/ms.Rnw
Draft schematic for fig 1
Updates to manuscript and figures

\begin{figure*}
\centering
\includegraphics{figures/fig1.pdf}
\caption{three possible functional curves of plant mortality. Estimating growth. Cross validation proceedure}
\label{fig1}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics{figures/fig2.pdf}
\caption{Average logarithmic loss $\pm$ 95\% BCIs from 10-fold cross validation. (A) Stage 1: Comparing three functional forms of tropical tree mortality using absolute diameter growth (red) and basal area growth (blue). (B) Comparing model with and without species random effects. (C) Comparing all combinations of wood density effects.}
\label{fig2}
\end{figure}

@@

@@

\begin{figure}
\centering
\includegraphics{figures/fig3.pdf}
\caption{Average logarithmic loss $\pm$ 95\% BCIs from 10-fold cross validation. (A) Stage 1: Comparing three functional forms of tropical tree mortality using absolute diameter growth (red) and basal area growth (blue). (B) Comparing model with and without species random effects. (C) Comparing all combinations of wood density effects.}
\label{fig3}
\end{figure}

@@

\acknow{
J.C was supported by the Science and Industry Endowment Fund (SIEF; RP04-174). M.W was supported by a fellowship from the Australian Research Council (ARC). D.F. was supported by an ARC discovery grant. We thank Lachlan McCalman and Daniel Steinberg for statistical advice; Anias Gibert etc etc.}

>>>>

\begin{figure}
\centering
\includegraphics{figures/fig1.pdf}
\caption{Outline of methodology. A) Three functional forms of plant mortality. B) Past growth used to predict future mortality. C) Cross validation proceedure}
\label{fig1}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{figures/fig2.pdf}
\caption{Average logarithmic loss from 10-fold cross validation. (A) Example logarithmic loss curve for a single observed death. B) Comparing various functional forms of tropical tree mortality with different growth measures different (white = no growth, grey = basal area growth, black = dbh growth) and species effects. (C) Comparing model forms with various combinations of wood density effects.}
\label{fig2}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{figures/fig3.pdf}
\caption{Estimated log baseline mortality against wood density. Points are individual species and solid line is the mean trendline. All errors are $\pm$ 95\% BCI.}
\label{fig3}
\end{figure}

\begin{figure}
\centering
\includegraphics{figures/fig4.pdf}
\caption{Estimated curves of instantaneous mortality rate and annual mortality probability. A,C) Highlight expected response curves for a hypothetical median species at low (0.3) and high (0.8) wood density. B,D) Predicted response curves for all species. Errors are $\pm$ 95\% BCI.}
\label{fig4}
\end{figure}

@@

@@

\acknow{
J.C was supported by the Science and Industry Endowment Fund (SIEF; RP04-174). M.W was supported by a fellowship from the Australian Research Council (ARC). D.F. was supported by an ARC discovery grant. We thank Lachlan McCalman and Daniel Steinberg for statistical advice; Anias Gibert etc etc.  Fig. 1a uses images by Tracey Saxby, IAN Image Library (http://ian.umces.edu/imagelibrary)}
